Title

### 2024-06-26 paper/main.tex
Updates

Using this mixed data partial association measure, we propose an iterative DAG
modification / construction procedure. Users can start with an empty graph.
Given a DAG $ G $ and a dataset $ D $, for each pair for variable $ X $ and $ Y
$ in $ G $ that does not have an edge between them, we compute the partial
association measure: $ \rho(X, Y; pa_G(X) \cup pa_G(Y)) $. Additionally, for
each pair of variable in $ G $, that has an edge between them in we compute the
partial association measure: $ \rho(X, Y; pa_{\underline{G}}(X) \cup
pa_{\underline{G}}(Y) $. In the case of no edge, this measure of association
can be interpreted as the unexplained

Any two variables in a DAG that do not have an edge between them imply a
conditional independence test that is they are independent given the parents of
both the variables, $ X \ci Y | pa(X) \cup pa(Y) $. In the case of model
testing, a CI statement like this can be used to check whether the assumption
of the model holds in the data or is violated. For mixed data, a few different
CI tests have been proposed such as likelihood-ratio based, and residualization
based. However, if we just use the CI test to check the p-value we cannot use
it to find the modification that is able to improve the score the most. We can
however use the measure of association to check which assocation between the
variables in the data is not explained by the model. Using this the expert can
decide to add an edge between the variables but will need to choose the
direction of the edge.

\begin{theorem}
If we have access to an oracle that can give correct edge directions, the
algorithm above is consistent.
\end{theorem}

\section{Web Tool}
\label{sec:web}
Based on the approach outlined in the previous section, we built a web-based
tool that researchers can upload their dataset to and apply this method to
interactively draw models. Users can start by uploading their datasets. The web
interface should then automatically show them all the correlated variables in a
graphical representation. The red colored edges represent potential new edge
between the variables.

\todo[inline]{List some of the features of the online platform}

>>>>

% Add that we need a p-value as well.

Using this mixed data partial association measure, we propose an iterative DAG
modification / construction procedure. Users can start with an empty graph.
Given a DAG $ G $ and a dataset $ D $, for each pair for variable $ X $ and $ Y
$ in $ G $ that does not have an edge between them, we compute the partial
association measure: $ \rho(X, Y; pa_G(X) \cup pa_G(Y)) $. The measure of
assocation in this case can be interpreted as the unexplained observed
association between them given the current model. We can then use this to rank
pair of variables which have very high unexplained association between them.
Based on the domain expertise, the user can then choose one of these suggested
pair of variables, decide the direction of the edge between the variables, and
add it to the model. Once the new edge is added we can recompute the assocation
of all other variables and $ X $ and $ Y $.

Additionally, in each iteration of modification, for each pair of variable in $
G $, that has an edge between them in we compute the partial association
measure: $ \rho(X, Y; pa_{\underline{G}}(X) \cup pa_{\underline{G}}(Y) $. This
measure of assocation can be interpreted as the strength of the edge between
the variables. If the value of this assocation below a certain threshold, we
can remove the edge.

\begin{theorem}
	If we have access to an oracle that can give correct edge directions, taking a
	greedy approach with the produre above results in the correct graph
	being recovered.
\end{theorem}

\section{Web Tool}
\label{sec:web}
Based on the procedure outlined in the previous section, we built a web-based
tool that allows users to interactively create/modify their model. The user
starts by uploading their dataset and optionally the initial DAG. If no initial
DAG is provided an empty graph is initialized. The tool also computes the
Shipley's C value at any point. The web-tool would automatically show all
unexplained assocations in the DAG by adding red edges between them. The edge
weight of the edge represents how high this strength is. Users can also set the
threshold for p-value and association to control how many edges are shown at a
time. Based on these shown potential edges, the user can select the edge that
they want to add and decide the direction for it. If the tool detects an
incorrect edge in the graph, it is shown in black. Once the user is happy with
the graph they have they can export it into different formats to use it for
further computation.
